\subsection{Social Implications }
A very popular topic in current technologies 'Big-data' has made users more conscious of how companies store and manipulate data. Users are less comfortable using cameras and microphones to monitor their actions. An extremely popular device used by consumers is the 'Amazon Echo' a range of voice assistant controlled devices. Amazon has reportedly sold over 100 million Amazon Alexa devices. By the end of 2018 it was reported there are 22 billion internet of things (IoT) devices. Computer consoles such as the  Nintendo Wii and the Xbox Kinect incorporated gestures since 2006 both selling over 35 million units overall. Over the last decade, traditional consoles use consoles by mainstream leaving a large majority of games unsupported due to the social refusal of using gestured based controls. China has been implementing facial recognition used to publicly shame jaywalkers and toilet paper thieves in China which is a prime example of how smart cities are changing how people interact and act as a society. As written by Chris Horn for the Irish times ' Hands off: Covid-19 is fuelling a boom in touchless technology' due to the explosion of the covid-19 virus companies are investing in touch-less gestures to prevent staff or users from sharing the same surface.
  




\subsection{Modeling gestures}
Creating a standard model for gestures using the human body can be extremely tricky due to language barriers and modeling the suitability. For example, the gesture 'thumbs up' has a different rude meaning in the middle east. The system for modeling the gesture must use a robust scaling system to integrate body Gesture Modelling.


\begin{enumerate}
   \item Modeling Techniques 
   \begin{itemize}
     \item \textbf{ Machine Learning :} As defined by SAS Institute - 'Machine learning is a method of data analysis that automates analytical model building. It is a branch of artificial intelligence based on the idea that systems can learn from data, identify patterns and make decisions with minimal human intervention.'
     
       \item \textbf{ Artificial  intelligence :} As defined by Oxford - 'the theory and development of computer systems able to perform tasks normally requiring human intelligence, such as visual perception, speech recognition, decision-making, and translation between languages.'

   \end{itemize}
\end{enumerate}




